\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\geometry{letterpaper, margin=1in}
\title{\textbf{Working Draft Outline: Paper 2 \\ Transfer-Field Conversion Route}}
\author{Stephen Breighner}
\date{March 2026}
\begin{document}
\maketitle

\section*{Status}
This draft outline covers the more ambitious branch: introduce a transfer field or conversion channel that mediates how collapsing matter enters the condensate description.

\section*{Core Scope}
\begin{itemize}[leftmargin=1.25em]
  \item Define a trigger for the transition from baryonic collapse to condensate behavior.
  \item Introduce a transfer field, rate law, or conversion medium that is absent from the first paper.
  \item Track what happens to conserved quantities during the transition.
  \item Show how the new mechanism changes observational predictions beyond the effective-potential model.
\end{itemize}

\section*{Proposed Flow}
\begin{enumerate}[leftmargin=1.4em]
  \item Start from the limits of the conservative effective-description paper.
  \item Define the transfer field and the threshold variables that activate it.
  \item Write the production, saturation, and escape terms for the condensate build-up.
  \item Clarify conservation-law bookkeeping and any residual observable signatures.
  \item Compare this branch against the purely effective route to show what new explanatory power is gained.
\end{enumerate}

\section*{Required Clarifications}
\begin{itemize}[leftmargin=1.25em]
  \item What quantity acts as the order parameter for phase change?
  \item Is the field fundamental, emergent, or only phenomenological?
  \item What observables distinguish this route from standard compact-object collapse?
\end{itemize}

\section*{Near-Term Deliverable}
A second paper that moves from ``effective end-state'' to ``transition mechanism,'' with explicit acknowledgement that this branch is more speculative and requires additional field dynamics.

\end{document}
